A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-05 manuscript.Rmd
add more details to release. Spelling out your thoughts in more detail

GitHub has a "release" function, which creates a link to a specific version of your project, where everything is available as a zip file.
You have the opportunity to describe the release in the release notes and to upload other additional files (e.g. the rendered pdf).

>>>>

In software development, a release is the distribution of a piece of computer software indicating a certain maturity in development and level of completeness.  GitHub has a "release" function, which creates a link to a specific snapshot of your project that then is available as a single compressed file. We believe that the idea of software releases can be leveraged for singling out important versions in a research project. We found it useful to label the following stages of development as release:
- Preregistration (repository contains the final data analysis plan; also see the Section on PAC)
- Completion of data collection (repository contains all study data)
- Preprint (repository exactly reproduces a preprint that is hosted externally)
- Submission or Resubmission (repository exactly reproduces a given version (re)submitted to a journal)
- In Press (repository exactly reproduces the final manuscript as accepted by a scientific journal)

You have the opportunity to describe the release in more detail in the accompanying release notes and to add extra files (e.g., complementing the Markdown source code of a journal article with a rendered PDF document).
